\documentclass[a4paper,10pt]{article}
\usepackage[top=0.75in, bottom=0.75in, left=0.50in, right=0.75in]{geometry}
\usepackage{palatino}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage[colorlinks=true, urlcolor=blue, urlbordercolor={0 1 1}]{hyperref}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{color}
\definecolor{mygrey}{gray}{0.75}
\textheight=9.75in
\raggedbottom

\setlength{\tabcolsep}{0in}
\newcommand{\lsep}{-0.5cm}

\pagestyle{empty}
%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\small \colorbox{mygrey}{\begin{minipage}{0.975\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage} \hspace{0.2cm}}}}
\newcommand{\ressubheading}[3]{
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} r}
	\textsc{{\textbf{#1}}} & \textsc{\textit{[#2]}} \\
\end{tabular*}\vspace{-8pt}}
%-----------------------------------------------------------

\begin{document}
\indent \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lr}
\multirow{3}{*}{\huge\textsc{\textbf{Abhijeet Dubey}}}	& \textbf{Email:} \href{mailto:dubey.abhijeet09@gmail.com}{dubey.abhijeet09@gmail.com}				\\
							& \textbf{Website:} \href{https://github.com/dracarys09/?tab=repositories}{github.com/dracarys09/}	\\
							& \textbf{Phone:} +91 947 949 5532
\end{tabular*}

\resheading{\textbf{ACADEMIC DETAILS}}\\[\lsep]
\\ \\
\indent \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}cccc}
\hline
\textbf{Year}	&	\textbf{Degree / Certificate}			&	\textbf{University / School}	&	\textbf{CPI / \%}	\\
\hline
2019 (expected)	&	M. Tech (Computer Science and Engineering)	&	IIT Bombay			&	8.05 / 10		\\[0.15cm]
2016		&	B. Tech (Computer Science and Engineering)	&	IIIT Jabalpur		&	8.4 / 10		\\[0.15cm]
2012		&	Class XII (CBSE)				&	Maharishi Vidya Mandir, Jabalpur&	92.2 \%		\\[0.15cm]
2010		&	Class X (CBSE)					&	Maharishi Vidya Mandir, Jabalpur&	9.2/10		\\
\hline
\end{tabular*}
\\ \\
\indent \resheading{\textbf{FIELDS OF INTEREST}}\\[\lsep]
\\ \\
\indent \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lll}
  Machine Learning & Algorithms\\
\end{tabular*}
\\
\indent \resheading{\textbf{INTERNSHIPS}}\\[\lsep]
\\ \\
\indent\small{\textbf{Google Summer of Code}}	\hfill	\small{\textit{(May'17 - Aug'17)}} \\
\indent\small{\textbf{Software Developer, Intern}}
\begin{itemize}
\item \noindent \small{Currently working with \textit{The Linux Foundation} and implementing a common print dialog that will enable users to print documents easily.}
\\[-0.5cm]
\item \noindent \small{Developing a backend for common printing dialog using google cloud print API to facilitate printing on google cloud printers from anywhere using any device.}
\item \noindent \small{\textit{Project Link:} \href{https://goo.gl/dr7YQG}{Google Cloud Print Backend} }
\end{itemize}

\indent\small{\textbf{Oracle Corporation}}	\hfill	\small{\textit{(Jun'15 - Nov'15)}} \\
\indent\small{\textbf{Software Developer, Intern}}
\begin{itemize}
\item \noindent \small{Used tabular testing tools like Synergy to develop robust test scripts and produced better results in less time.}
\\[-0.5cm]
\item \noindent \small{Designed and developed test suite to perform smoke testing of Oracle's SIM software.}
\end{itemize}

\indent \small{\textbf{Uddhat Softwares Pvt. Ltd.}}	\hfill	\small{\textit{(Jun'14 - Jul'14)}} \\
\indent \small{\textbf{Web Developer, Intern}}
\begin{itemize}
\item \noindent \small{Developed an online marketplace offering tasks and services.}
\\[-0.5cm]
\item \noindent \small{\textit{Technologies:} PHP, MySQL, HTML, CSS, Bootstrap3, Laravel4, Javascript}
\end{itemize}

\indent \resheading{\textbf{PROJECTS}}\\[\lsep]
\\ \\
\indent\small{\textbf{Music Generation Using LSTM}}	\hfill	\small{\textit{(Feb'17 - Apr'17)}}
\begin{itemize}
 \item Used RNN and LSTM based approach to synthesize music frames for Piano music and Electronic Dance Music (EDM).
 \item Used Tensorflow to train LSTM based model on audio samples to synthesize music from two widely different genres using their STFT features.
 \item Used AdaDelta optimization method to minimize mean squared loss between the ground truth feature vector and the predicted feature vector.
 \item \textit{Project Report: } \href{https://goo.gl/wSzUxP}{Music Generation using LSTM}
\end{itemize}

\indent\small{\textbf{Intelligent Carrom Player}} \hfill	\small{\textit{(Oct'16 - Nov'16)}}
\begin{itemize}
 \item Used continuous actor-critic methods and reinforcement learning techniques and developed an agent that can play carrom both in one player and two player setting.
 \item Implemented a policy network that takes current state as input and and produces three action components namely striker's position, angle and force as outputs.
 \item Our best agent clears the board in 23 turns on average in single player mode.
 \item \textit{Project Report: } \href{https://goo.gl/2Csvi8}{Designing an Intelligent Carrom Player}
\end{itemize}

\indent\small{\textbf{Music Genre Classification}}	\hfill	\small{\textit{(Feb'17 - Apr'17)}}
\begin{itemize}
 \item Used classifiers like Decision Tree, Random Forests, Multi Class Neural Network to classify music genres.
 \item Trained our models on \textit{GTZAN} dataset consisting of 1000 audio samples of 30 seconds each.
 \item We were able to achieve 63.5\% accuracy using only timbral features which was an improvement of 2.5\% over the original \textit{GTZAN Music Genre Classification Paper}.
 \item \textit{Project Report: } \href{https://goo.gl/dTFD85}{Music Genre Classification}
\newline
\newline
\end{itemize}


\indent\small{\textbf{OJ (ACM ICPC Style Online Judge)}}	\hfill	\small{\textit{(Oct'16 - Nov'16)}}
\begin{itemize}
 \item Used MVC architecture and Laravel(PHP framework) along with MaterializeCSS to develop ACM ICPC style online judge.
 \item \href{https://github.com/dracarys09/oj}{https://github.com/dracarys09/oj}
\end{itemize}

\indent\small{\textbf{Recommending Accounts to Twitter Users}}	\hfill	\small{\textit{(Mar'15 - Apr'15)}}
\begin{itemize}
 \item Used machine learning techniques like collaborative filtering and clustering to develop a smart web interface which suggests interesting twitter accounts to follow.
 \item Used 3-NN to predict 3 most interesting accounts to follow.
\end{itemize}


\resheading{\textbf{IMPORTANT COURSES UNDERTAKEN}}\\[\lsep]
\\ \\
\indent \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lll}
Foundations of Machine Learning		&	Automatic Speech Recognition	&	Foundations of Intelligent \& Learning Agents \\
Design \& Analysis of Algorithms	&	Linear Algebra			&	Game Theory
\end{tabular*}

\resheading{\textbf{TOOLS \& LIBRARIES}}\\[\lsep]
\\
\begin{itemize}
 \item \textbf{Languages: } C/C++(advanced), Python(advanced), PHP(beginner), Javascript(beginner)
 \item \textbf{Frameworks: } Tensorflow(beginner), Laravel
 \item \textbf{Tools: } git, sed, awk, gdb, GnomeBuilder, \LaTeX

\end{itemize}

\resheading{\textbf{ACHIEVEMENTS}}\\[\lsep]
\\
\begin{itemize}
 \item Qualified for onsite regionals of \textbf{ACM ICPC} for Amritapuri Regionals in 2015.
 \item Awarded \textbf{Certificate of Merit} two times for exceptional academic achievements during freshmen year and sophomore year.
 \item \textbf{1}$^{st}$ place in Obfuscated 2015 (programming competition).
 \item \textbf{Won Bronze Medal} in National Round of iURL, held at IIT Bombay in March 2014.
 \item My team (Paradigm Shift) was ranked \textbf{748} out of more than 32000 teams in TCS CodeVita 2015.

\end{itemize}


\end{document}
